data exploration

### 2021-04-19 outputs/exploratory.Rmd
Complete lit review section, scale validity section. Refine graphs and tables. Expand outcomes of interest section. Add coefficents and CIs to in-text model results. Add replications for first gen only, H/B only, impact of race on ISR, and relationship between similarity, ISR, and outcomes.

>>>>

```{r s1simcorrelation, echo=FALSE, warning=FALSE, message=FALSE}
# Make the summary stats part of the table
summary <- expdata %>% 
  dplyr::select(treatment, 
                s1_sim1, s1_sim2, s1_sim3, s1_sim4, s1_sim5, s1_sim6) %>%
  summary_factorlist("treatment", 
                     c("s1_sim1", "s1_sim2", "s1_sim3", "s1_sim4", "s1_sim5", "s1_sim6"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = FALSE,
                     add_row_totals = TRUE,
                     include_row_missing_col = TRUE,
                     col_totals_rowname = "",
                     total_col = TRUE,
                     col_totals_prefix = "N (%) = ") %>%
  dplyr::select("Total N", "Missing N", "Total")

# Make the correlation matrix part of the table
matrix <- data.frame(apaCorr(as.matrix(expdata %>% 
                  dplyr::select(s1_sim1, s1_sim2, s1_sim3, s1_sim4, s1_sim5, s1_sim6))))

# Combine the summary and correlation tables
table <- summary %>%
  bind_cols(matrix) %>%
  rename("Mean (SD)" = Total, N = "Total N", Missing = "Missing N")

# Put in a table.
table %>%
  kable(caption = "Correlation matrix for initial student similarity scale",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down"))
```

```{r s1tsrcorrelation, echo=FALSE, warning=FALSE, message=FALSE}
# Make the summary stats part of the table
summary <- expdata %>% 
  dplyr::select(treatment, 
                s1_tsr1, s1_tsr2, s1_tsr3, s1_tsr4, s1_tsr5, s1_tsr6, s1_tsr7) %>%
  summary_factorlist("treatment", 
                     c("s1_tsr1", "s1_tsr2", "s1_tsr3", "s1_tsr4", "s1_tsr5", "s1_tsr6", "s1_tsr7"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = FALSE,
                     add_row_totals = TRUE,
                     include_row_missing_col = TRUE,
                     col_totals_rowname = "",
                     total_col = TRUE,
                     col_totals_prefix = "N (%) = ") %>%
  dplyr::select("Total N", "Missing N", "Total")

# Make the correlation matrix part of the table
matrix <- data.frame(apaCorr(as.matrix(expdata %>% 
                  dplyr::select(s1_tsr1, s1_tsr2, s1_tsr3, s1_tsr4, s1_tsr5, s1_tsr6, s1_tsr7))))

# Combine the summary and correlation tables
table <- summary %>%
  bind_cols(matrix) %>%
  rename("Mean (SD)" = Total, N = "Total N", Missing = "Missing N")

# Put in a table.
table %>%
  kable(caption = "Correlation matrix for initial student similarity scale",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down"))
```

```{r s2simcorrelation, echo=FALSE, warning=FALSE, message=FALSE}
# Make the summary stats part of the table
summary <- expdata %>% 
  dplyr::select(treatment, 
                s2_sim1, s2_sim2, s2_sim3, s2_sim4, s2_sim5, s2_sim6) %>%
  summary_factorlist("treatment", 
                     c("s2_sim1", "s2_sim2", "s2_sim3", "s2_sim4", "s2_sim5", "s2_sim6"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = FALSE,
                     add_row_totals = TRUE,
                     include_row_missing_col = TRUE,
                     col_totals_rowname = "",
                     total_col = TRUE,
                     col_totals_prefix = "N (%) = ") %>%
  dplyr::select("Total N", "Missing N", "Total")

# Make the correlation matrix part of the table
matrix <- data.frame(apaCorr(as.matrix(expdata %>% 
                  dplyr::select(s2_sim1, s2_sim2, s2_sim3, s2_sim4, s2_sim5, s2_sim6))))

# Combine the summary and correlation tables
table <- summary %>%
  bind_cols(matrix) %>%
  rename("Mean (SD)" = Total, N = "Total N", Missing = "Missing N")

# Put in a table.
table %>%
  kable(caption = "Correlation matrix for initial student similarity scale",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down"))
```

```{r s2tsrcorrelation, echo=FALSE, warning=FALSE, message=FALSE}
# Make the summary stats part of the table
summary <- expdata %>% 
  dplyr::select(treatment, 
                s2_tsr1, s2_tsr2, s2_tsr3, s2_tsr4, s2_tsr5, s2_tsr6, s2_tsr7) %>%
  summary_factorlist("treatment", 
                     c("s2_tsr1", "s2_tsr2", "s2_tsr3", "s2_tsr4", "s2_tsr5", "s2_tsr6", "s2_tsr7"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = FALSE,
                     add_row_totals = TRUE,
                     include_row_missing_col = TRUE,
                     col_totals_rowname = "",
                     total_col = TRUE,
                     col_totals_prefix = "N (%) = ") %>%
  dplyr::select("Total N", "Missing N", "Total")

# Make the correlation matrix part of the table
matrix <- data.frame(apaCorr(as.matrix(expdata %>% 
                  dplyr::select(s2_tsr1, s2_tsr2, s2_tsr3, s2_tsr4, s2_tsr5, s2_tsr6, s2_tsr7))))

# Combine the summary and correlation tables
table <- summary %>%
  bind_cols(matrix) %>%
  rename("Mean (SD)" = Total, N = "Total N", Missing = "Missing N")

# Put in a table.
table %>%
  kable(caption = "Correlation matrix for initial student similarity scale",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down"))
```

```{r t2tsrcorrelation, echo=FALSE, warning=FALSE, message=FALSE}
# Make the summary stats part of the table
summary <- expdata %>% 
  dplyr::select(treatment, 
                t2_tsr1, t2_tsr2, t2_tsr3, t2_tsr4, t2_tsr5, t2_tsr6, t2_tsr7) %>%
  summary_factorlist("treatment", 
                     c("t2_tsr1", "t2_tsr2", "t2_tsr3", "t2_tsr4", "t2_tsr5", "t2_tsr6", "t2_tsr7"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = FALSE,
                     add_row_totals = TRUE,
                     include_row_missing_col = TRUE,
                     col_totals_rowname = "",
                     total_col = TRUE,
                     col_totals_prefix = "N (%) = ") %>%
  dplyr::select("Total N", "Missing N", "Total")

# Make the correlation matrix part of the table
matrix <- data.frame(apaCorr(as.matrix(expdata %>% 
                  dplyr::select(t2_tsr1, t2_tsr2, t2_tsr3, t2_tsr4, t2_tsr5, t2_tsr6, t2_tsr7))))

# Combine the summary and correlation tables
table <- summary %>%
  bind_cols(matrix) %>%
  rename("Mean (SD)" = Total, N = "Total N", Missing = "Missing N")

# Put in a table.
table %>%
  kable(caption = "Correlation matrix for initial student similarity scale",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down"))
```

```{r}
expdata %>%
  dplyr::select(treatment, 
                s1_sim, s1_tsr, s2_sim, s2_tsr, t2_sim1, t2_tsr, 
                grade, std_grade, t2_finalexam, ir_f16_gpa, f17_enrolled, 
                s1_female, n_course) %>%
  missing_pattern()
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
substudentsecondsimilaritymodel <- lm(data = expdata %>% filter(s_firstgen == 1),
                                     formula = s2_sim ~ treatment + n_course + race_match + gend_match + age_dif,
                                     na.action = na.omit)
substudentsecondrelationshipmodel <- lm(data = expdata %>% filter(s_firstgen == 1),
                                     formula = s2_tsr ~ treatment + n_course + race_match + gend_match + age_dif,
                                     na.action = na.omit)
substdgrademodel <- lm(data = expdata %>% filter(s_firstgen == 1),
                      formula = grade ~ treatment + ir_f16_gpa + n_course + race_match + gend_match + age_dif,
                                     na.action = na.omit)
```

```{r submodeltable, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
# Make table to display model results
stargazer(substudentsecondsimilaritymodel,
          substudentsecondrelationshipmodel,
          substdgrademodel,
          title = "Additional model results",
          align = TRUE,
          no.space = TRUE,
          omit.stat=c("ser","f"),
          column.sep.width = "-10pt",
          label = "tab:modeltable",
          type = "latex",
          header = FALSE,
          dep.var.labels = c("Student Similarity 2",
                             "Student ISR 2",
                             "Standardized course grade"),
          covariate.labels = c("Treatment",
                               "CGPA", 
                               "Course size",
                               "Matching racial self-ID", "Matching gender self-ID", "Age difference")
          )
```
